SunPy - Python for Solar Physics

### 2014-01-19 2-Data_Types.tex
changes and images

>>>>

\subsection{Visualisation}
As has been demonstrated in this section, the core SunPy datatypes include 
visualisation code that is specialised to that data type. These visualisation 
methods all currently utilise the matplotlib package, and are designed in such 
a way that they integrate well with the pyplot functional interface of 
matplotlib, as demonstrated in Listing \ref{code:mpl_1}.

\begin{listing}[h]
\begin{minipage}{0.49\columnwidth}
\begin{minted}{python}
import sunpy.map
import matplotlib.pyplot as plt

#Read in a aia file using SunPy
aiamap = sunpy.map.Map('aia.fits')

#Create the figure and axis 
#explicitly
fig = plt.figure()
ax = plt.subplot()

#Create a image plot with raw data
im = ax.imshow(aiamap.data,...)
#add a colour bar
plt.colorbar(im,ax=ax)

#Add a title
plt.title("My AIA plot")
plt.show()
\end{minted}
\end{minipage}
\begin{minipage}{0.49\columnwidth}
\begin{minted}{python}
import sunpy.map
import matplotlib.pyplot as plt

#Read in a aia file using SunPy
aiamap = sunpy.map.Map('aia.fits')

#Create the figure and axis 
#explicitly
fig = plt.figure()
ax = plt.subplot()

#Plot the AIA map
im = aiamap.plot(axes=ax)
#add a colour bar
plt.colorbar(im,ax=ax)

#Add a title
plt.title("My AIA plot")
plt.show()
\end{minted}
\end{minipage}
\caption{A simple example of how SunPy's plotting functions provide similar 
behaviour to matplotlib's pyplot interface.}
\label{code:mpl_1}
\end{listing}

This design philosophy makes the behaviour of SunPy's visualisation routines 
intuitive to those who already understand how matplotlib's interface is 
designed as well as allowing the use of the standard matplotlib commands to 
change the plot, \textit{e.g.} set the title.
